Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-28 cosmic_voids.tex
FA profiles analysis. Section 5, results, done

In left panels of Fig. \ref{fig:RhoVel} we compute density profiles of 
voids stacked according to their size and their compensation index. 
Instead of calculating the radial internal structure inside an effective
radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
to capture the properties of neighbour structures as well.

@@

>>>>

In left panels of Fig. \ref{fig:RhoVel} we compute density profiles of 
voids stacked according to their size and their compensation index. 
Instead of calculating the radial internal structure inside the effective
radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
to capture the properties of neighbour structures as well.

@@

Finally, we also calculate FA profiles in right panels of Fig. \ref{fig:RhoVel}.
A very interesting result from this is a very clear distinction between
the internal profile, below the effective radius, and the external profile. 
For subcompensated voids, they reach quickly the background 
value after $1\reff$. On the other hand, overcompensated voids reach a FA 
ridge at the same radius and then the background value. Central values are
in agreement with those of the density and velocity fields, where larger 
voids exhibit more isotropic cores, associated to higher outflows rates 
and low mass concentrations.

The difference between the radius where the density ridge is reached 
($r\sim 2-4\hMpc$ depending on the void size), and the radius of the FA 
ridge ($r\sim 1-1.5\hMpc$ for all voids) reinforces our previous 
conclusions: before reaching high-density structures like filaments and 
cluster, high-anisotropic, middle-density walls are reached, so the FA 
ridge should be chosen as the natural frontier of voids instead of the
density ridge. This choosing would produce smaller voids as compared with
other voids finding methods, however contamination from external structures
is also avoided.
